An efficient composition of bidirectional programs by tupling and lazy updates

### 2019-11-29 paper/6.related-work.tex
capitalize Section titles
add references

\subsubsection*{BX languages and implementations}

@@

\subsubsection*{Optimization techniques}

Memoization \cite{} is well-known technique to reduce extra evaluation. In our case, simple application of memoization $put_m$ works well for many BX programs.
Another way to reduce extra evaluation is fusion \cite{Wadler:1988:DTP:80099.80104}. However, fusion of BX programs are not considered well \textcolor{red}{(really?)}. Therefore we did not use this way.
  Instead of that, we introduce another way that uses tupling \cite{Fokkinga90}, lazy update and lazy computation \cite{}. Tupling is often used for reducing common evaluations, but we use it for reducing the size of complements.
  Lazy evaluation is also a well-known and widly-used optimization technique to reduce the redundant evaluation. Because we use OCaml for implementation, we need to introduce this explicitly. If we use Haskell, a lazy evaluated language, we do not need to introduce them.

@@

%Tupling \cite{tupling} is an optimization technique by combining several computations. Although tupling is usually used for reducing the evaluation cost\cite{}, we use it to reduce the size of the things need to keep.

@@

%Lazy evaluation \cite{} is well-known and widly-used optimization technique to reduce the redundant evaluation. Because we use OCaml for implementation, we need to introduce this explicitly. If we use Haskell, a lazy evaluated language, we do not need to introduce them.

>>>>

\subsubsection*{BX Languages and Implementations}

@@

\subsubsection*{Optimization Techniques}

Memoization \cite{Bellman:2003:DP:862270,MICHIE1968} is well-known technique to reduce extra evaluation. In our case, simple application of memoization $put_m$ works well for many BX programs.
Another way to reduce extra evaluation is fusion \cite{Wadler:1988:DTP:80099.80104}. However, fusion of BX programs are not considered well \textcolor{red}{(really?)}. Therefore we did not use this way.
  Instead of that, we introduce another way that uses tupling \cite{Fokkinga90}, lazy update and lazy computation \cite{Henderson:1976:LE:800168.811543, Hudak:2007:HHL:1238844.1238856}. Tupling is often used for reducing common evaluations, but we use it for reducing the size of complements.
  Lazy evaluation is also a well-known and widly-used optimization technique to reduce the redundant evaluation. Because we use OCaml for implementation, we need to introduce this explicitly. If we use Haskell, a lazy evaluated language, we do not need to introduce them.

@@

%Tupling \cite{tupling} is an optimization technique by combining several computations. Although tupling is usually used for reducing the evaluation cost, we use it to reduce the size of the things need to keep.

@@

%Lazy evaluation is well-known and widly-used optimization technique to reduce the redundant evaluation. Because we use OCaml for implementation, we need to introduce this explicitly. If we use Haskell, a lazy evaluated language, we do not need to introduce them.
